Test data

### 2022-07-21 Shiny/Test/Flexdashboard rows.Rmd
KPIs.

### KPI 3
```{r}
valueBoxOutput("KPI_box3")
```

@@

@@

  # Creating KPI_admin value
  KPI_admin <- reactive({
    exceldata() |>
      mutate(
        KPI_admin =
          str_c( # Using str_c() to concatenate value and % sign
            format( # shortening(lengthening) the resulting value
              # calculating the value
              (expenses_administrative / expenses_program_services * 100),
              digits = 3
            ), "%"
          )
      ) |>
      filter(year == max(year)) |> # selecting latest available year
      select(KPI_admin) |> # dropping all other variables
      str_flatten() # turning into a single string
  })

@@

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "Admin spend",
      color = met.brewer("Troy", n = 1),
      icon = "fa-random"
    )
  })

@@

  # Duplicate value boxes for testing
  output$KPI_box3 <- renderValueBox({
    valueBox(
      value = str_c(format(KPI_fundraising_num(), digits = 3), "%"),
      caption = "primary",
      color = "primary",
      icon = "fas fa-coffee"
    )
  })

@@

  output$balance_plotly <- renderPlotly(
    ggplotly(balance_plot())
  )
})
```

>>>>

### KPI 3
```{r}
valueBoxOutput("KPI_box_OPX")
```

@@

### Expenses
```{r}
plotlyOutput("expenses_plotly")
```

@@

  # Creating KPI_admin value
  KPI_admin <- reactive({
    exceldata() |>
      mutate(
        KPI_admin =
          str_c( # Using str_c() to concatenate value and % sign
            format( # shortening(lengthening) the resulting value
              # calculating the value
              (expenses_administrative / (expenses_program_services +
                                            expenses_administrative +
                                            expenses_fundraising +
                                            expenses_other) * 100),
              digits = 3
            ), "%"
          )
      ) |>
      filter(year == max(year)) |> # selecting latest available year
      select(KPI_admin) |> # dropping all other variables
      str_flatten() # turning into a single string
  })

@@

  # Creating OPX KPI
  KPI_OPX_num <- reactive({
    exceldata() |> 
      filter(year == max(year)) |> 
      transmute(
        KPI_OPX = (revenue_private_contributions + revenue_investments +
                 assets_cash_in_bank_and_cash_equivalents) /
      (liability_short_term_grants_payable +
         liability_revocable_endowments +
         liability_long_term_grants_payable) * 100
      ) |> 
      pull()
  })

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "Administration as a % of total expenses",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })

@@

  # KPI_OPX
  output$KPI_box_OPX <- renderValueBox({
    valueBox(
      value = str_c(format(KPI_OPX_num(), digits = 3), "%"),
      caption = "Liquid assets / obligations",
      color = ifelse(KPI_OPX_num() <= 100, "success", "danger"),
      icon = "fas fa-coffee"
    )
  })

  # Duplicate value boxes for testing

@@

  output$balance_plotly <- renderPlotly(
    ggplotly(balance_plot())
  )

  #----Expenses---------------------------------------
  expenses_plot <- reactive({
    exceldata() |> 
  transmute(
    Year = as.factor(year),
    Other = expenses_other,
    Administrative = expenses_administrative,
    Fundraising = expenses_fundraising,
    `Program services` = expenses_program_services
  ) |> 
  pivot_longer(c(Other:`Program services`), names_to = "Expenses") |> 
  mutate(
    Expenses = ordered(Expenses, levels =
                         c("Program services", "Administrative",
                         "Fundraising", "Other")) 
  ) |> 
  ggplot(aes(Year, value, fill = Expenses)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = label_dollar()) +
  scale_fill_met_d("Troy")
  })

  output$expenses_plotly <- renderPlotly(
    ggplotly(expenses_plot())
  )
})
```

### 2022-07-21 Shiny/Test/Test data.Rmd
KPIs.

### `View()`
```{r view, eval=FALSE}
View(kreft_html)
View(kreft_excel)
```

### kabled
```{r}
kreft_html
kreft_excel
```

@@

annual_profit
balance_positive

@@

### Overhead
```{r}

```{r}

>>>>

### `View()`
```{r view, eval=FALSE}
View(kreft_html_with_variables)
View(kreft_excel)
```

### kabled
```{r}
kreft_html
kreft_excel
kreft_html_with_variables

@@

### Expenses
```{r}
kreft_excel |> 
  transmute(
    Year = as.factor(year),
    Other = expenses_other,
    Administrative = expenses_administrative,
    Fundraising = expenses_fundraising,
    `Program services` = expenses_program_services
  ) |> 
  pivot_longer(c(Other:`Program services`), names_to = "Expenses") |> 
  mutate(
    Expenses = ordered(Expenses, levels =
                         c("Program services", "Administrative",
                         "Fundraising", "Other")) 
  ) |> 
  ggplot(aes(Year, value, fill = Expenses)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = label_dollar()) +
  scale_fill_met_d("Troy")

kreft_excel |> 
  transmute(
    Year = as.factor(year),
    Administrative = expenses_administrative,
    Fundraising = expenses_fundraising,
    `Program services` = expenses_program_services,
    Other = expenses_other
  )
?as_factor
```

@@

### Private donation growth
```{r}
kreft_excel |> 
  select(year, revenue_private_contributions) |> 
  pivot_wider(names_from = year, values_from = revenue_private_contributions) |> 
  mutate(
    growth = `2020` / `2019` * 100
  )

?pivot_wider
```

### Their KPI

```{r}
# private contributions, investments, cash in bank / short-term garnts payable, revocable endowments, long-term grants payable

mutate(kreft_excel,
    KPI_OPX = (revenue_private_contributions + revenue_investments +
                 assets_cash_in_bank_and_cash_equivalents) /
      (liability_short_term_grants_payable +
         liability_revocable_endowments +
         liability_long_term_grants_payable) * 100
  ) |> select(year, KPI_OPX)

kreft_excel |> 
  filter(year == max(year)) |> 
      transmute(
        KPI_OPX = (revenue_private_contributions + revenue_investments +
                 assets_cash_in_bank_and_cash_equivalents) /
      (liability_short_term_grants_payable +
         liability_revocable_endowments +
         liability_long_term_grants_payable) * 100
      ) |> 
      pull()
```
